MGRFE: multilayer recursive feature elimination based on an embedded genetic algorithm for cancer classification

### 2019-05-02 MGRFE-TCBB-2018-08-16/MGRFE-tcbb.tex
Second response.

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{url}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{amsthm,amsmath}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{fullpage}
\usepackage{float}
\usepackage[colorlinks,allcolors=black]{hyperref}
\usepackage[nocompress]{cite}
\renewcommand{\arraystretch}{1.05}

@@

	\begin{table*}[t]
		\centering
		\caption{Performance comparison between McTwo and MGRFE on 17 datasets in Dataset One}
		\label{Tab:CMP McTwo RST}
		\resizebox{1.0\textwidth}{!}{
			\begin{tabular}{llllllllllllllllll}
				\toprule
				& DLBCL & Pros & Colon & Leuk & Mye & ALL1 & ALL2 & ALL3 & ALL4 & CNS & Lym & Adeno & Gas & Gas1 & Gas2 & T1D & Stroke\\
				\midrule
				MGRFE \(Acc\) & 1.0 & 0.981 & 0.985 & 1.0 & 0.937 & 1.0 & 0.910 & 0.927 & 0.990 & 1.0 & 1.0 & 1.0 & 1.0 & 0.980 & 1.0 & 0.911 & 1.0\\
				McTwo \(Acc\) & 1.0 & 0.95 & 0.9 & 1.0 & 0.85 & 1.0 & 0.75 & 0.8 & 0.88 & 0.85 & 1.0 & 1.0 & 0.97 & 0.95 & 1.0 & 0.81 & 0.85\\
				MGRFE Genes & 3 & 3 & 6 & 2 & 7 & 1 & 8 & 8 & 6 & 7 & 3 & 1 & 3 & 3 & 2 & 7 & 4\\
				McTwo Genes & 4 & 3 & 6 & 2 & 7 & 1 & 2 & 5 & 2 & 4 & 4 & 2 & 3 & 4 & 2 & 6 & 1\\
				\bottomrule
		\end{tabular}}
	\end{table*}

@@

	The genes selected by MGRFE also have close relevance to the phenotypes in gene expression datasets. The genes selected by MGRFE with the 100\% 5-fold CV $Acc$ on datasets Leuk, Gas, and ALL1 are only two genes, three genes, and one gene, respectively.
	For each gene selected by MGRFE on these three datasets, we surveyed the number of published literatures involving the gene of interest and the related cancer phenotype in PubMed on 9th July, 2018. The literature-mining results on these three datasets are shown in Table \ref{Tab:mining}. Moreover, the gene probes finally selected by MGRFE on all 19 datasets are provided in the S5 section of the Supplementary Material.
	In the Leukaemia dataset, our selected genes are \textit{CD33} and \textit{TCF3}. In PubMed, there are 3001 published literatures about \textit{CD33}, among which 1753 (58.94\%) papers discuss the relevance of \textit{CD33} to leukemia. And there are 569 publications about \textit{TCF3} in PubMed, among which 115 (20.21\%) papers confirming the association between \textit{TCF3} and leukemia. According to GeneCards, the E protein encoded by \textit{TCF3} performs a critical function in lymphopoiesis and is necessary for B and T lymphocytes. This gene is related to cancers including ALL (t(1;19), with \textit{PBX1}), childhood leukemia (t(19;19), with \textit{TFPT}), and acute leukemia (t(12;19)). In the Gastric dataset, genes \textit{COL8A1}, \textit{SEMA6D}, and \textit{LIFR} are selected by MGRFE, and there are 187 publications in PubMed confirming their relevance to cancer, but only five papers reveal their relations with gastric cancer. According to the excellent classification performance of these three genes on gastric cancer, they could be novel biomarker candidates for gastric cancer. In the ALL1 dataset, only one gene, \textit{CD3D}, is selected by MGRFE. There are 84 publications in PubMed about \textit{CD3D}, among which 13 (15.48\%) papers revealing the relevance of \textit{CD3D} to leukemia. In ref. \cite{Y34}, it has also been pointed out that gene \textit{CD3D} is one ideally discriminatory feature and gave a diagnostic rule when the expression of \textit{CD3D} is below a certain cutoff limit. Regarding \textit{CD3D}, GeneCards explains that this gene is involved in T-cell development and signal transduction, whereas defects in this gene will lead to severe combined immunodeficiency.

@@

	Furthermore, the biological associations with phenotypes using literature mining in PubMed for the selected genes confirmed that the genes selected by MGRFE are biologically relevant to cancer phenotypes. Therefore, the informative genes selected by MGRFE could be novel biomarker candidates that are useful for better understanding the molecule mechanism related to the phenotypes. Moreover, for clinical applications involving microarrays, MGRFE can contribute to the development of a potential simplified procedure for diagnosis of cancer subgroups by selecting the minimal discriminatory gene subsets, which will cut down the cost of medical diagnoses.

@@

	The authors would like to thank the National Natural Science Foundation of China [Grant number 61472158, 71774154] and the Natural Science Foundation of Jilin Province (20180101331JC).

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran}
\usepackage{url}
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{multirow}
\usepackage{amsthm,amsmath}
\usepackage{graphicx}
\usepackage{ragged2e}
\usepackage{fullpage}
\usepackage{float}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage[colorlinks,allcolors=black]{hyperref}
\usepackage[nocompress]{cite}
\renewcommand{\arraystretch}{1.05}

@@

	\begin{table*}[t]
		\centering
		\caption{Performance comparison between McTwo and MGRFE on 17 datasets in Dataset One}
		\label{Tab:CMP McTwo RST}
		\resizebox{1.0\textwidth}{!}{
			\begin{tabular}{llllllllllllllllll}
				\toprule
				& DLBCL & Pros & Colon & Leuk & Mye & ALL1 & ALL2 & ALL3 & ALL4 & CNS & Lym & Adeno & Gas & Gas1 & Gas2 & T1D & Stroke\\
				\midrule
				MGRFE \(Acc\) & 1.0 & 0.981 & 0.985 & 1.0 & 0.937 & 1.0 & 0.910 & 0.927 & 0.990 & 1.0 & 1.0 & 1.0 & 1.0 & 0.980 & 1.0 & 0.911 & 1.0\\
				McTwo \(Acc\) & 1.0 & 0.95 & 0.9 & 1.0 & 0.85 & 1.0 & 0.75 & 0.8 & 0.88 & 0.85 & 1.0 & 1.0 & 0.97 & 0.95 & 1.0 & 0.81 & 0.85\\
				MGRFE Genes & 3 & 4 & 6 & 2 & 7 & 1 & 8 & 8 & 6 & 7 & 3 & 1 & 3 & 3 & 2 & 7 & 4\\
				McTwo Genes & 4 & 3 & 6 & 2 & 7 & 1 & 2 & 5 & 2 & 4 & 4 & 2 & 3 & 4 & 2 & 6 & 1\\
				\bottomrule
		\end{tabular}}
	\end{table*}

@@

	The genes selected by MGRFE also have close relevance to the phenotypes in gene expression datasets. The genes selected by MGRFE with the 100\% 5-fold CV $Acc$ on datasets Leuk, Gas, and ALL1 are only two genes, three genes, and one gene, respectively.
	For each gene selected by MGRFE on these three datasets, we surveyed the number of published literatures involving the gene of interest and the related cancer phenotype in PubMed on 9th July, 2018. The literature-mining results on these three datasets are shown in Table \ref{Tab:mining}. Moreover, the gene probes finally selected by MGRFE on all 19 datasets are provided in the "S5" section of the Supplementary Material.
	In the Leukaemia dataset, our selected genes are \textit{CD33} and \textit{TCF3}. In PubMed, there are 3001 published literatures about \textit{CD33}, among which 1753 (58.94\%) papers discuss the relevance of \textit{CD33} to leukemia. And there are 569 publications about \textit{TCF3} in PubMed, among which 115 (20.21\%) papers confirming the association between \textit{TCF3} and leukemia. According to GeneCards, the E protein encoded by \textit{TCF3} performs a critical function in lymphopoiesis and is necessary for B and T lymphocytes. This gene is related to cancers including ALL (t(1;19), with \textit{PBX1}), childhood leukemia (t(19;19), with \textit{TFPT}), and acute leukemia (t(12;19)). In the Gastric dataset, genes \textit{COL8A1}, \textit{SEMA6D}, and \textit{LIFR} are selected by MGRFE, and there are 187 publications in PubMed confirming their relevance to cancer, but only five papers reveal their relations with gastric cancer. According to the excellent classification performance of these three genes on gastric cancer, they could be novel biomarker candidates for gastric cancer. In the ALL1 dataset, only one gene, \textit{CD3D}, is selected by MGRFE. There are 84 publications in PubMed about \textit{CD3D}, among which 13 (15.48\%) papers revealing the relevance of \textit{CD3D} to leukemia. In ref. \cite{Y34}, it has also been pointed out that gene \textit{CD3D} is one ideally discriminatory feature and gave a diagnostic rule when the expression of \textit{CD3D} is below a certain cutoff limit. Regarding \textit{CD3D}, GeneCards explains that this gene is involved in T-cell development and signal transduction, whereas defects in this gene will lead to severe combined immunodeficiency.

@@

	To conclude, the chief research contribution in theory is providing a novel feature selection method which combines embedded genetic algorithm with recursive feature elimination process, working as a creative thought for future research. To the best of our knowledge, none previous studies have designed an evolutionary algorithm using variable length integer encoding approach in a recursive manner to deal with the problem of minimal discriminatory feature selection in high-dimension datasets, which is described in this paper. Meanwhile, through theoretical and experimental comparisons, our proposed MGRFE could outperform mostly other state-of-the-art algorithms for gene selection on microarray data. Therefore, the proposed method MGRFE is worthy to be generalized to more feature selection problems on high-dimensional data characterized by the ”large \textit{p} small \textit{n}” paradigm and applied in several practical fields.

	Furthermore, our presented MGRFE would be useful in medical diagnosis as well as further biomedical research. The biological associations with phenotypes using literature mining in PubMed for the selected genes confirmed that the genes selected by MGRFE are biologically relevant to cancer phenotypes. Therefore, the informative genes selected by MGRFE could be novel biomarker candidates that are useful for better understanding the molecule mechanism related to the phenotypes and developing potential early detection and molecularly-targeted therapies for cancer diseases. Moreover, for clinical applications involving microarrays, MGRFE can contribute to the development of a potential simplified procedure for diagnosis of cancer subgroups by selecting the minimal discriminatory gene subsets, which will cut down the cost of medical diagnoses.

@@

	The authors would like to thank the National Natural Science Foundation of China [Grant number 61472158, 71774154] and the Natural Science Foundation of Jilin Province (20180101331JC).
	Also, we are grateful to the two revered reviewers for their constructive comments.
